NOSQL\\ BEST PRACTICES

### 2018-03-26 pgconfus2018/presentation.tex
More slides with too much info about document structure
More slides & examples

\usetheme[]{m}

@@

@@

@@

    \ifx\inserttitle\@empty\else
    {{% \inserttitle is nonempty
      \raggedright%
      %\linespread{1.0}%
      \usebeamerfont{title}%
      \usebeamercolor[fg]{title}%
      %\vspace*{1.3em}
      \if@noSmallCapitals%
        \inserttitle%
      \else%
        \scshape{\color{black} \textbf{\begin{center}NOSQL FOR\\POSTGRESQL\end{center}}}%
      \fi%
      \vspace*{0.3em}
    }}
    \fi

@@

\title{NOSQL INSIDE SQL}
\subtitle{BEST PRACTICES}
\date{\today}
\author{DMITRY DOLGOV}
\institute{}

@@

\fontsize{17pt}{19}\selectfont
\section{}

@@

@@

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Jsonb <-> Relation}

        \vspace{20pt}

        \column{0.5\textwidth}
        \begin{itemize}[leftmargin=*]
            \item \includegraphics[width=6cm,height=5cm]{document.jpg}
        \end{itemize}
        \end{columns}

@@

>>>>

\usetheme[]{metropolis}

@@

\usepackage{tcolorbox}
\usepackage{tabularx}
\usepackage{array}
\usepackage{colortbl}
\tcbuselibrary{skins}

@@

\newcommand\tikzmark[1]{%
  \tikz[overlay,remember picture] \coordinate (#1);}

@@

    \ifx\inserttitle\@empty\else
    {{% \inserttitle is nonempty
      \raggedright%
      %\linespread{1.0}%
      \usebeamerfont{title}%
      \usebeamercolor[fg]{title}%
      %\vspace*{1.3em}
      \if@noSmallCapitals%
        \inserttitle%
      \else%
        \scshape{\color{black} \textbf{\begin{center}\inserttitle\end{center}}}%
      \fi%
      \vspace*{0.3em}
    }}
    \fi

@@

\title{NOSQL\\ BEST PRACTICES}
\subtitle{FOR POSTGRESQL}
\date{\today}
\author{DMITRY DOLGOV}
\institute{}

@@

@@

\fontsize{17pt}{18}\selectfont

@@

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Jsonb -> Relation}

        \begin{columns}[T,onlytextwidth]
        \column{0.5\textwidth}
        \begin{itemize}[leftmargin=*]
            \item \includegraphics[width=6cm,height=5cm]{document.jpg}
        \end{itemize}

        \column{0.5\textwidth}
        \begin{itemize}[leftmargin=*]
            \item \includegraphics[width=6cm,height=5cm]{relation.png}
        \end{itemize}

        \end{columns}

@@

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Complicated conditions}

        \begin{itemize}[label={\MVRightarrow}]
            \item jsquery
            \item SQL/JSON
        \end{itemize}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Complicated conditions}

        \inputminted[
            fontsize=\normalsize,
        ]{sql}{sql/complex_where_jsquery.sql}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Complicated conditions}

        \inputminted[
            fontsize=\normalsize,
        ]{sql}{sql/complex_where_standard.sql}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Complicated select}

        \inputminted[
            fontsize=\normalsize,
        ]{sql}{sql/complex_select.sql}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Jsonb -> Relation}

        \begin{columns}[T,onlytextwidth]
        \column{0.3\textwidth}
        \begin{itemize}[leftmargin=*]
            \item \includegraphics[width=4cm,height=4cm]{document.jpg}
        \end{itemize}

        \column{0.3\textwidth}
        \begin{itemize}[leftmargin=*]
            \item \includegraphics[width=4cm,height=4cm]{schema.jpg}
        \end{itemize}

        \column{0.3\textwidth}
        \begin{itemize}[leftmargin=*]
            \item \includegraphics[width=4cm,height=4cm]{relation.png}
        \end{itemize}

        \end{columns}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Constraints}

        \begin{itemize}[label={\MVRightarrow}]
            \item Simple checks for value, type or size
            \item More convenient checks with jsquery
            \item Json schema
        \end{itemize}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Constraints}

        \begin{itemize}[label={\MVRightarrow}]
            \item Simple checks for value, type or size
            \item More convenient checks with jsquery
            \item Json schema
        \end{itemize}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Constraints}

        \inputminted[
            fontsize=\normalsize,
        ]{sql}{sql/constraints.sql}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Relation -> Jsonb}

        \column{0.5\textwidth}
        \begin{itemize}[leftmargin=*]
            \item \includegraphics[width=6cm,height=5cm]{document.jpg}
        \end{itemize}

        \end{columns}

        \inputminted[
            fontsize=\large,
        ]{sql}{sql/jsonb_agg.sql}

\fontsize{13pt}{14}\selectfont
\section{Seamless interaction\\ between json and relation}
\fontsize{17pt}{18}\selectfont

\fontsize{17pt}{19}\selectfont
\begin{frame}
    \frametitle{}
    \begin{center}

    \inputminted[
        fontsize=\Large,
    ]{json}{sql/with_array_data.json}

\fontsize{17pt}{19}\selectfont
\begin{frame}
    \frametitle{}
    \begin{center}

    \begin{overprint}
    \onslide<1>
    \inputminted[
        fontsize=\Large,
        escapeinside=||
    ]{sql}{sql/with_array.sql}

    \onslide<2>
    \inputminted[
        fontsize=\Large,
        escapeinside=||
    ]{sql}{sql/with_array_highlight.sql}
    \end{overprint}

    \inputminted[
        fontsize=\large,
    ]{bash}{sql/with_array.sh}

\fontsize{17pt}{19}\selectfont
\begin{frame}
    \frametitle{}
    \begin{center}

    \inputminted[
        fontsize=\Large,
    ]{json}{sql/iterate_document_data.json}

\fontsize{17pt}{19}\selectfont
\begin{frame}
    \frametitle{}
    \begin{center}

    \begin{overprint}
    \onslide<1>
    \inputminted[
        fontsize=\Large,
        escapeinside=||
    ]{sql}{sql/iterate_document.sql}

    \onslide<2>
    \inputminted[
        fontsize=\Large,
        escapeinside=||
        ]{sql}{sql/iterate_document_highlight.sql}
    \end{overprint}

    \inputminted[
        fontsize=\large,
    ]{bash}{sql/iterate_document.sh}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Place for ID}

        \begin{itemize}[label={\MVRightarrow}]
            \item Inside a document
            \item As as separate column
        \end{itemize}

        \includegraphics[width=0.75\textwidth,center]{pg_id_place.png}

\begin{frame}
    \frametitle{}
    \begin{center}
        \textbf{Multiple jsonb columns}

        \begin{itemize}[label={\MVRightarrow}]
            \item Keep at the end for readability
            \item tuple\_deform
        \end{itemize}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Multiple jsonb columns}

        \vspace{1cm}
        \begin{tcolorbox}[adjusted title= Table]
        \begin{tabular}{c|c|c|c|c|c}
            \tikzmark{start} value & \tikzmark{right} value & value & value & value & value... \\\hline
        value & value & value & value & value & value... \\\hline
        \tikzmark{end} value & value & value & value & value & value...
        \end{tabular}
        \end{tcolorbox}

        \begin{tikzpicture}[overlay,remember picture]
            \draw[->, line width=1mm]
            let \p1=(start), \p2=(end) in ($(\x1,\y1)+(-1.2,0.2)$) -- node[] {} ($(\x1,\y2)+(-1.2,0.0)$);
        \end{tikzpicture}

        \begin{tikzpicture}[overlay,remember picture]
            \draw[->, line width=1mm, color=white]
            let \p1=(start), \p2=(right) in ($(\x1,\y1)+(1.5,1.3)$) -- node[] {} ($(\x1,\y2)+(12.0,1.3)$);
        \end{tikzpicture}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Multiple jsonb columns}

        \vspace{1cm}
        \begin{tcolorbox}[adjusted title= Table]
        \begin{tabular}{c|c|c|c|c|c}
        \tikzmark{start} value... & \tikzmark{right} value & value & value & value & value \\\hline
        value... & value & value & value & value & value \\\hline
        \tikzmark{end} value... & value & value & value & value & value
        \end{tabular}
        \end{tcolorbox}

        \begin{tikzpicture}[overlay,remember picture]
            \draw[->, line width=1mm]
            let \p1=(start), \p2=(end) in ($(\x1,\y1)+(-1.2,0.2)$) -- node[] {} ($(\x1,\y2)+(-1.2,0.0)$);
        \end{tikzpicture}

        \begin{tikzpicture}[overlay,remember picture]
            \draw[->, line width=1mm, color=white]
            let \p1=(start), \p2=(right) in ($(\x1,\y1)+(1.5,1.3)$) -- node[] {} ($(\x1,\y2)+(12.0,1.3)$);
        \end{tikzpicture}
